Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-09 paper/paper.tex
pass on comments (wip)

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of some standard JS
function\Mar{is this correct? what are those?}. We
found that different engines often check the pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a pre-condition that another engine does not\Mar{why is that?
that should not happen if the spec was fully documented and engines
properly implemented those checks. Explain and give example.}. In those cases,
our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category. \Mar{show real examples of
  HI and LO.}
\Mar{can we detect dups mining issue trackers?}

@@

\subsection{Seed JS files\label{sec:seeds}}~We considered test suites
associated with all four JS engines we analyzed
(section~\ref{sec:methodology:engines}). In addition, we mined tests
from other GitHub repositories based on the following selection
criteria--the project must have received at least 1K stars and the
project must not use external libraries. Figure~\ref{fig:query}
illustrates the GitHub API query~\cite{github-rest-api} we used to
find javascript engines projects defined by the keyword
``javascript-engine''\Mar{is this a label or two keywords?}.  The
resulting list included a total of 33 projects.  A total of \Fix{4?}
projects remained after removing projects that \Fix{...}.\Mar{explique
como o numero baixou tanto.}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites\Mar{try to use a single
      name (if possible) to facilitate reference in the paper. Use the
  full path in the URL (citation) to indicate where one can find those
  files.}}
  \begin{tabular}{ccr}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    Duktape & \cite{duktape} & 997 \\
    JerryJS & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\
    Mozilla & \Fix{??} & 32,414 \\
    V8.test.benchmarks.data & \Fix{??} & 64 \\
    WebKit.jstests.es6 & \Fix{??} & 605 \\
    WebKit.jstests.microbenchmarks & \Fix{??} & 426 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}

>>>>

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}, \Igor{crashes (ie. FatalError) and core dumps 
  are considered HI group as well}. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of some standard JS
function.
\Mar{is this correct? what are those?}\Igor{Yeah, it's okay}We
found that different engines often check the pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a pre-condition that another engine does not, 
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
\Igor{these cases happen because the specification describes how a function
should work, however the internal implementation is defined by the engine developers}.
In those cases,
our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category. \Mar{show real examples of
  HI and LO.}
\Igor{For example, a bug caught by our environment and reported as LO priority was reported 
on Chakra engine, the JS code can be found in Figure~\ref{fig:lo-priority}. In this case,
this is a seed from Mozilla suite (\CodeIn{mozilla/non262/statements/for-in-with-assignments.js}),
the warning was not caught by the \CodeIn{assertEq} function that compares if two arguments are equals, 
the bug appears inside the generator function\footnote{Generators \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Statements/function*}}
at line 2. According to ES6 specification\footnote{ES6 YieldExpression \url{https://www.ecma-international.org/ecma-262/8.0/index.html\#prod-YieldExpression}},
it is allowed the use of \CodeIn{yield in} in a \CodeIn{for} loop. In our infrastructure,
only Chakra engine fails with an error output \CodeIn{SyntaxError: Syntax error}, due
the output does not shows nothing related with assertions, we considered this one as a warning from LO group.
Until now, the issue was confirmed and waiting for merge/closed.
\Fix{checar ate o prazo de submissao. Essa issue esta confirmada e com commits, falta apenas o merge.}
}
\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function},
  }
  \begin{lstlisting}
function* g1() {
  for (var x = yield in {}) ;
}
var it = g1();
assertEq(it.next().done, false);
assertEq(it.next().done, true);
  \end{lstlisting}
  \normalsize
  \caption{Bug caught by our environment as LO priority.}
  \label{fig:lo-priority}
  \end{figure}

An example of a warning from the HI group is defined in Figure~\ref{fig:hi-priority}. 
This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
integer 3 to a big integer number. We reported this case in chakra due a core dumps that occurs
during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
this is an intentional behavior of engine that crash the process if it runs out of memory
\footnote{Chakra issue \#4979 \url{https://github.com/Microsoft/ChakraCore/issues/4979}}.

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
function test() {
  return typeof String.prototype.repeat === "function"
    && "foo".repeat(657604378) === "foofoofoo";
}
if (!test())
  throw new Error("Test failed");
  \end{lstlisting}
  \normalsize
  \caption{Warning captured as HI priority.}
  \label{fig:hi-priority}
  \end{figure}

\Mar{can we detect dups mining issue trackers?}
\Igor{
  acho que encontrar duplicatas seria um estudo a parte, devido a linguagem natural.
  Tenho umas consideracoes:
  \begin{itemize}
    \item warning HI possui a msg "Error: Test Failed", nao tem como buscar algo com isso, 
    se for pegar a linha que falhou, provavelmente vai mostrar a linha onde o assert se encontra.
    \item warning LO: podemos tentar conseguir buscar pelo output/funcao que falhou,
    \item O fuzzinator tem algo similar (dei uma olhada rapida, nao eh complicado)
  \end{itemize}
}

@@

\subsection{Seed JS files\label{sec:seeds}}~We considered test suites
associated with all four JS engines we analyzed
(section~\ref{sec:methodology:engines}). In addition, we mined tests
from other GitHub repositories based on the following selection
criteria--the project must have received at least 1K stars and the
project must not use external libraries. Figure~\ref{fig:query}
illustrates the GitHub API query~\cite{github-rest-api} we used to
find javascript engines projects defined by the label
``javascript-engine''.  The resulting list included a total of 33 projects.
\Igor{
  Due the GitHub does not supports to get the repository files via API, we
  analyzed manually each of them. It was observed that sixteen projects
  are invalid for us due the uses NodeJS that our engine cannot support it,
  empty repositories and browser support as well and another 13 projects 
  does not have a test module in their repository.
  A total of 4 projects remained after the manual inspection, two of them
  are added before, for example the V8\footnote{The official mirror of the V8 Git repository \url{https://github.com/v8/v8}}
  and V7\footnote{V7 Embedded JavaScript engine \url{https://github.com/cesanta/v7}} repositories.
  The Duktape and JerryScript tests are the seeds that we integrate on our infraestruture.
  The repositories of JSI and TinyJS are found manually and was incorpored also even less 1K of stars.
}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites\Mar{try to use a single
      name (if possible) to facilitate reference in the paper. Use the
  full path in the URL (citation) to indicate where one can find those
  files.}}
  \begin{tabular}{ccr}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    Duktape & \cite{duktape} & 997 \\
    JerryScript & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\
    Mozilla & \Fix{??} & 32,414 \\
    V8.test.benchmarks.data & \Fix{??} & 64 \\
    WebKit.jstests.es6 & \Fix{??} & 605 \\
    WebKit.jstests.microbenchmarks & \Fix{??} & 426 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}
